---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ZIPGSK

<!-- badges: start -->
[![R-CMD-check](https://github.com/tsnm1/ZIPGSK/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tsnm1/ZIPGSK/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/tsnm1/ZIPGSK/branch/main/graph/badge.svg)](https://app.codecov.io/gh/tsnm1/ZIPGSK?branch=main)
[![Codecov test coverage](https://codecov.io/gh/tsnm1/ZIPGSK/graph/badge.svg)](https://app.codecov.io/gh/tsnm1/ZIPGSK)
<!-- badges: end -->

Zero Inflated Poisson-Gamma based Simultaneous knockoff (ZIPGSK) is a novel method proposed for enhancing multi-source count data. This method is primarily based on the Gaussian copula framework of the zero-inflated Poisson–Gamma (ZIPG) distribution for knockoff generation. It is combined with the Simultaneous Knockoff method to address variable selection in multi-source data. 

The research conducted in this project is based on the preprint paper titled "ZIPG-SK: A Novel Knockoff-Based Approach for Variable Selection in Multi-Source Count Data".

## Installation

You can install the development version of ZIPGSK from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tsnm1/ZIPGSK")
```

## Example

Here is a basic example of how to solve a common problem in variable selection during the implementation of ZIPGSK:

```{r example}
# library(ZIPGSK)
# library(pscl)
# library(knockoff)
# library(ZIPG)
# library(MASS)

## basic example code

data(data_pg_copula)
i <- 2 # or 1
data_K_j <- data_pg_copula[[i]] 
count_K_j <- data_K_j # [data_K_j[,1]==c,]
n_x1 <- 3
data_x <- as.data.frame(count_K_j[, c(1:n_x1 + 1)])
W <- as.data.frame(count_K_j[, -c(1:(n_x1 + 2))])
M <- count_K_j[, n_x1 + 2]
n_w <- dim(W)[1]
n_data <- 2
y <- rep(rep(c(1, 2), n_data), rep(n_w / 2 / n_data, n_data * 2))
class_K <- rep(c(1:n_data), rep(n_w / n_data, n_data))
n_p  <-  c(40,50)
n_p_all <- c(400,500)
T_var <- 1:n_p[i]
name_data <- names(table(class_K))

fdr <- 0.2

# ZIPG_DE_S3 <- ZIPG_SK(
#   W = W, class_K = class_K, data_x = data_x, M = M, y = y, T_var = T_var,
#   fdr = fdr, test_statistic = "DE", filter_statistics = 1
# )
# ZIPG_DE_S3$FDRPower
# i <- 1, 0.20 0.19 0.72  
# i <- 2, 0.20 0.22 0.78  

```


## Simulated data generation

In general, our package also includes a function (simulate_datasets_3) that can simulate the generation of multi-source count data. An example is provided below:

```{r} 
# data_pg_copula <- simulate_datasets_3(
#   times = 1, n_data = 2, n_1_all = c(400, 400), n_p_all = c(50, 100, 400), n_p = c(10, 20, 40),
#   diff = 0, prob_max = 0.5, marginal1 = "pg", copula1 = TRUE, fc1 = 1,
# )
# i = 1 # i = 1:3;
# data_K_j = data_pg_copula[[1]][[1]][[i]][[1]][[1]] # i = 1,2;
```

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. -->

<!-- You can also embed plots, for example: -->

<!-- ```{r pressure, echo = FALSE} -->
<!-- # plot(pressure) -->
<!-- ``` -->

<!-- In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN. -->
